---
title: "Browsing the PhysioRecipes case database"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Browsing the PhysioRecipes case database}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

PhysioRecipes is a version-controlled **database of reproducible analysis case
studies** on public physiological data. Each case states a proposition, answers
a question on a public dataset, and runs through to figures and a conclusion,
with every reported number traced to an artifact and the whole operation DAG
replayable byte-identically.

This package ships the verified run bundles plus a small API to *browse* the
corpus. This vignette uses only that bundled metadata -- it is fully offline and
does **not** replay any case.

```{r setup}
library(PhysioRecipes)
```

## The corpus at a glance

`list_cases()` returns one row per case: its modality, the ecosystem packages it
exercises, the dataset, the reproducibility status, and how many reported claims
are grounded.

```{r list}
cases <- list_cases()
nrow(cases)
head(cases[, c("id", "modality", "status", "n_grounded", "n_claims")])
```

How many cases per modality and status:

```{r tabulate}
sort(table(cases$status), decreasing = TRUE)
head(sort(table(cases$modality), decreasing = TRUE))
```

## Opening one case

`get_case()` parses a case's `case.json`; `case_path()` and `case_bundle()`
resolve its files on disk.

```{r open}
id <- cases$id[1]
case <- get_case(id)
case$title
case$proposition
# The verified evidence bundle (prereg, op-DAG, artifact, claims, report):
list.files(case_bundle(id))
```

## Checking the invariants

`validate_cases()` applies the structural gate every case must satisfy (public
dataset, every claim grounded, a byte-identical replay recorded). Here we check
the first few; omit `ids` to gate the whole corpus.

```{r validate}
validate_cases(ids = head(cases$id, 5))
```

## The research queue

Some cases escalate an unresolved question to a paper. `escalations()` lists
them (public cases keep this empty by embargo):

```{r escalate}
escalations()
```

## Where to go next

* `?list_cases` / `?get_case` -- browse and open cases.
* `?validate_cases` -- the invariants gate.
* `?case_bundle` -- the on-disk evidence a reader re-runs or audits; the same
  bundle shape `PhysioLake::physioPutBundle()` stores with lineage.
